# outpack.server

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![R build status](https://github.com/mrc-ide/outpack.server/workflows/R-CMD-check/badge.svg)](https://github.com/mrc-ide/outpack.server/actions)
[![Build status]()](https://buildkite.com/mrc-ide/outpack-dot-server?branch=main)
[![codecov.io](https://codecov.io/github/mrc-ide/outpack.server/coverage.svg?branch=main)](https://codecov.io/github/mrc-ide/outpack.server?branch=main)
<!-- badges: end -->

This is an implementation of the [outpack](https://mrc-ide.github.io/outpack) HTTP API as an R package using [porcelain](https://reside-ic.github.io/porcelain/) and [plumber](https://docs.rstudio.com/resources/plumber/). We will probably replace this with a higher performance implementation later, but keep the interface the same.


```{r, include = FALSE}
```

## Usage

Assuming that you have an outpack repository at `path`:

```{r}
docker run -v ${PWD}:/outpack -p 8001:8001 mrcide/outpack.server:prototype /outpack
```

### Responses

```{r, results = "asis", echo = FALSE}
pkgload::load_all()

root <- create_temporary_root(use_file_store = TRUE)
ids <- create_random_packet_chain(root, 4)
obj <- api(root, log_level = "fatal")

id <- ids[[1]]
meta <- root$metadata(id)
hash <- meta$files$hash

commands <- list(
  list("GET", "/", NULL),
  list("GET", "/metadata/list", NULL),
  list("GET", "/metadata/<id>", sprintf("/metadata/%s", id)),
  list("GET", "/file/<hash>", sprintf("/file/%s", hash)))

do_response <- function(cmd) {
  method <- cmd[[1]]
  path_label <- cmd[[2]]
  path_use <- cmd[[3]] %||% path_label
  res <- obj$request(method, path_use)
  if (is.raw(res$body)) {
    response <- paste(c(head(res$body, 10), "..."), collapse = " ")
  } else {
    response <- jsonlite::prettify(res$body)
  }

  template <- "### %s %s\n\n```json%s```"
  sprintf(template, method, path_label, response)
}

txt <- vapply(commands, do_response, "")
cat(paste(txt, collapse = "\n\n"))
```

## Installation

To install `outpack.server`:

```r
remotes::install_github("mrc-ide/outpack.server", upgrade = FALSE)
```

## License

MIT © Imperial College of Science, Technology and Medicine
